|

### 2023-01-06 paper.Rmd
Fri Jan  6 14:00:08 CET 2023: update-remote.sh

```{bash compile_airfoil_2hl_maxIndSize_fullRun_30gens, include=FALSE}
bash /Users/rmn/masterThesis/eda-gp-2020/experiments/airfoil_2hl_maxIndSize_fullRun_30gens/re_evaluate_airfoil_2hl_maxIndSize_30gen.sh
```

>>>>

```{bash compile_airfoil_2hl_maxIndSize_fullRun_30gens, include=FALSE}
bash /Users/rmn/masterThesis/eda-gp-2020/experiments/airfoil_1hl_maxIndSize_fullRun_30gens/re_evaluate_airfoil_1hl_maxIndSize_30gen.sh

bash /Users/rmn/masterThesis/eda-gp-2020/experiments/airfoil_2hl_maxIndSize_fullRun_30gens/re_evaluate_airfoil_2hl_maxIndSize_30gen.sh

bash /Users/rmn/masterThesis/eda-gp-2020/experiments/energyCooling_2hl_maxIndSize_fullRun_30gens/re_evaluate_energyCooling_2hl_maxIndSize_fullRun_30gens.sh

# add new experiments for full runs here!
# ...
```
